%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Software Engineer II} % Job title
{NetApp} % Organization
{Sunnyvale, California} % Location
{March 2017 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Implemented checker transfer (internal tool) for cross-platform transfers.}
\item {Designed checkpoint restart for bi-directional backups to and from ONTAP to non-proprietary appliances.}
\item {Responsible for ONTAP data transfer code and ramping up the new hires on the team.}
\item {Added abort/hard abort work-flows for backups across different platforms.}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Software Engineer I} % Job title
{} % Organization
{} % Location
{September 2015 - March 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Worked on multi-threaded application that used a proprietary RPC protocol over TCP connections.}
\item {Optimized performance and efficiency of data transfers through cached socket connections.}
\item{Fixed various types of bugs and challenged myself to take on unfamiliar codepaths.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{NetApp Software Engineer Intern} % Job title
{NetApp} % Organization
{Sunnyvale, California} % Location
{June 2014 - September 2014} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Implemented and designed a new scalable feature into an existing code database.}
\item {Completed in-place configuration feature allowing customers to upgrade seamlessly.}
\item {Developed a better understanding for file systems and linux based operating systems.}
\end{cvitems} 
}

%------------------------------------------------

\cventry
{Instructional Student Assistant Workshop Facilitator} % Job title
{Cal Poly SLO} % Organization
{San Luis Obispo, California} % Location
{September 2012 - June 2014} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Facilitated Calculus workshop for classes on campus.}
\item {Practiced time management skills and experience working with others.}
\item {Gained leadership and communication skills.}
\end{cvitems}
}

%------------------------------------------------

% \cventry
% {Software Engineer} % Job title
% {ShitOne Corp. (Start-up company)} % Organization
% {Seoul, S.Korea} % Location
% {Dec. 2011 - Feb. 2012} % Date(s)
% { % Description(s) of tasks/responsibilities
% \begin{cvitems}
% \item {Developed a proxy drive smartphone application which connects proxy driver and customer. Implemented overall Android application logic and wrote API server for community service, along with lead engineer who designed bidding protocol on raw socket and implemented API server for bidding.}
% \end{cvitems}
% }

% %------------------------------------------------

% \cventry
% {Freelance Penetration Tester} % Job title
% {SAMSUNG Electronics} % Organization
% {S.Korea} % Location
% {Sep. 2013, Mar. 2011 - Oct. 2011} % Date(s)
% { % Description(s) of tasks/responsibilities
% \begin{cvitems}
% \item {Conducted penetration testing on SAMSUNG KNOX, which is solution for enterprise mobile security.}
% \item {Conducted penetration testing on SAMSUNG Smart TV.}
% \end{cvitems}
% }

%------------------------------------------------

\end{cventries}